---
title: "exp 2 data cleaning"
author: "K.G.Garner"
output: 
  pdf_document: default
  html_document: default
---

# this code 

### loads the raw data - assigns factors to variables etc, load functions
### conducts piecewise linear functions to the data (collapsed over blocks)
### removes trials up to the breakpoint
### saves data as a dataframe


```{r global_options, eval = TRUE, echo=FALSE}
knitr::opts_chunk$set(fig.width = 4, fig.height = 3, 
                      echo = FALSE, highlight = TRUE,
                      root.dir = "~/Dropbox/BHAMPROJECTS/RelValue_StudyProgramme/PROJECT_REPOSITORIES/ADDBIAS_REPOS/EXP2/ANALYSIS")
```


```{r load_raw_data, eval = TRUE, echo = FALSE}

source("clean_funcs.r")
source("trim_functions.R")
source("exp2_notepad-load_data.r")
rows = array()
rows$sub = levels(dat$sub) # start dataframe for row numbers
```


# block switches

As learning should be demonstrated by a speeding of RTs over the block, I am now going to plot the RTs by trial number (collapsed across all blocks and conditions conditions) after each block switch, and apply piecewise linear regression method to remove trials contaminated by the switch (i.e. remove trials occurring prior to the breakpoint).


```{r clean_switching_data_501, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-501'}
switch.rows = array()
switch.rows$sub = levels(dat$sub)

switch.rows$num[switch.rows$sub == "501"] = clean.out.block.switches(dat[dat$sub == "501",], 200)
```


```{r clean_switching_data_502, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-502'}
switch.rows$num[switch.rows$sub == "502"] = clean.out.block.switches(dat[dat$sub == "502",], 200)
```

```{r clean_switching_data_503, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-503'}
switch.rows$num[switch.rows$sub == "503"] = clean.out.block.switches(dat[dat$sub == "503",], 200)
```

```{r clean_switching_data_504, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-504'}
switch.rows$num[switch.rows$sub == "504"] = clean.out.block.switches(dat[dat$sub == "504",], 200)
```

```{r clean_switching_data_505, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-505'}
switch.rows$num[switch.rows$sub == "505"] = clean.out.block.switches(dat[dat$sub == "505",], 180)
```


```{r clean_switching_data_506, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-506'}
switch.rows$num[switch.rows$sub == "506"] = clean.out.block.switches(dat[dat$sub == "506",],170)
```


```{r clean_switching_data_507, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-507'}
switch.rows$num[switch.rows$sub == "507"] = clean.out.block.switches(dat[dat$sub == "507",],180)
```


```{r clean_switching_data_508, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-508'}
switch.rows$num[switch.rows$sub == "508"] = clean.out.block.switches(dat[dat$sub == "508",], 180)
```

```{r clean_switching_data_509, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-509'}
switch.rows$num[switch.rows$sub == "509"] = clean.out.block.switches(dat[dat$sub == "509",],190)
```


```{r clean_switching_data_510, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-510'}
switch.rows$num[switch.rows$sub == "510"] = clean.out.block.switches(dat[dat$sub == "510",], 140)
```

```{r clean_switching_data_511, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-511'}
switch.rows$num[switch.rows$sub == "511"] = clean.out.block.switches(dat[dat$sub == "511",], 200)
```


```{r clean_switching_data_512,  warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-512'}
switch.rows$num[switch.rows$sub == "512"] = clean.out.block.switches(dat[dat$sub == "512",], 200)
```


```{r clean_switching_data_513, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-513'}
switch.rows$num[switch.rows$sub == "513"] = clean.out.block.switches(dat[dat$sub == "513",], 190)
```


```{r clean_switching_data_514, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-514'}
switch.rows$num[switch.rows$sub == "514"] = clean.out.block.switches(dat[dat$sub == "514",], 180)
```

```{r clean_switching_data_515, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-515'}
switch.rows$num[switch.rows$sub == "515"] = clean.out.block.switches(dat[dat$sub == "515",], 180)

```


```{r clean_switching_data_516, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-516'}
switch.rows$num[switch.rows$sub == "516"] = clean.out.block.switches(dat[dat$sub == "516",], 180)

```

```{r clean_switching_data_517, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-517'}
switch.rows$num[switch.rows$sub == "517"] = clean.out.block.switches(dat[dat$sub == "517",], 200)

```

```{r clean_switching_data_518, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-518'}
switch.rows$num[switch.rows$sub == "518"] = clean.out.block.switches(dat[dat$sub == "518",], 130)

```

```{r clean_switching_data_519, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-519'}
switch.rows$num[switch.rows$sub == "519"] = clean.out.block.switches(dat[dat$sub == "519",], 200)

```

```{r clean_switching_data_520, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-520'}
switch.rows$num[switch.rows$sub == "520"] = clean.out.block.switches(dat[dat$sub == "520",], 180)

```

```{r clean_switching_data_521, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-521'}
switch.rows$num[switch.rows$sub == "521"] = clean.out.block.switches(dat[dat$sub == "521",], 200)

```

```{r clean_switching_data_522, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-522'}
switch.rows$num[switch.rows$sub == "522"] = clean.out.block.switches(dat[dat$sub == "522",], 200)

```

```{r clean_switching_data_523, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-523'}
switch.rows$num[switch.rows$sub == "523"] = clean.out.block.switches(dat[dat$sub == "523",], 200)

```

```{r clean_switching_data_524, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-524'}
switch.rows$num[switch.rows$sub == "524"] = clean.out.block.switches(dat[dat$sub == "524",], 200)

```

```{r clean_switching_data_525, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-525'}
switch.rows$num[switch.rows$sub == "525"] = clean.out.block.switches(dat[dat$sub == "525",], 200)

```

```{r clean_switching_data_526, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-526'}
switch.rows$num[switch.rows$sub == "526"] = clean.out.block.switches(dat[dat$sub == "526",], 200)

```


```{r rem_post_switch, eval = TRUE, echo = FALSE}
rem.post.switch <- function(data, rows){
  
  # __remove trials occurring prior to the break point__
    n_row = rows$num[rows$sub == data$sub[1]]
    trials = length(data$sub)
    mark.trials = array(data=0, dim=trials)
    for (x in 2:(trials - 25)){
      if (data$fixprob[x-1] != data$fixprob[x]){
        trials_rem = which(data$resp[c(x:(x+50))] == data$cor_resp[c(x:(x+50))])
        trials_rem = trials_rem[n_row]
        mark.trials[c(x:(x+trials_rem-1))] = 1
      }}
    data$mark = mark.trials
    data = data[data$mark < 1, ]
    return(data)
}

tmp = by(dat, dat$sub, rem.post.switch, switch.rows)
dat = as.data.frame(do.call(rbind, tmp))
rm(tmp)
```


```{r save_dat, warning = FALSE, echo = FALSE, eval = FALSE}
# save.image("exp2_clean_BS_v1_28_02_17.R")
```
