---
title: "exp 1 data cleaning"
author: "K.G.Garner"
output:
  pdf_document: default
  html_document: default
---

# this code 

### loads the raw data - assigns factors to variables etc, load functions
### conducts piecewise linear functions to the data (collapsed over blocks)
### removes trials up to the breakpoint
### saves data as a dataframe

```{r global_options, eval = TRUE, echo=FALSE}
knitr::opts_chunk$set(fig.width = 4, fig.height = 3, 
                      echo = TRUE, highlight = TRUE,
                      root.dir = "~/Dropbox/BHAMPROJECTS/RelValue_StudyProgramme/PROJECT_REPOSITORIES/ADDBIAS_REPOS/EXP1/ANALYSIS")
```


```{r load_raw_data, eval = TRUE, echo = FALSE}

source("clean_funcs.r")
source("trim_functions.R")
source("notepad-load_data.r")
rows = array()
rows$sub = levels(dat$sub) # start dataframe for row numbers
```

# block switches

As learning should be demonstrated by a speeding of RTs over the block, I am now going to plot the RTs by trial number (collapsed across all blocks and conditions conditions) after each block switch, and apply piecewise linear regression method to remove trials contaminated by the switch (i.e. remove trials occurring prior to the breakpoint).


```{r clean_switching_data_301, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-301'}
switch.rows = array()
switch.rows$sub = levels(dat$sub)

switch.rows$num[switch.rows$sub == "301"] = clean.out.block.switches(dat[dat$sub == "301",], 100)
```

```{r clean_switching_data_302, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-302'}

switch.rows$num[switch.rows$sub == "302"] = clean.out.block.switches(dat[dat$sub == "302",], 85)
```

```{r clean_switching_data_303, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-303'}
switch.rows$num[switch.rows$sub == "303"] = clean.out.block.switches(dat[dat$sub == "303",],85)
```

```{r clean_switching_data_304, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-304'}
switch.rows$num[switch.rows$sub == "304"] = clean.out.block.switches(dat[dat$sub == "304",], 95)
```

```{r clean_switching_data_305, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-305'}
switch.rows$num[switch.rows$sub == "305"] = clean.out.block.switches(dat[dat$sub == "305",],80)
```


```{r clean_switching_data_306, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-306'}
switch.rows$num[switch.rows$sub == "306"] = clean.out.block.switches(dat[dat$sub == "306",],85)
```


```{r clean_switching_data_307, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-307'}
switch.rows$num[switch.rows$sub == "307"] = clean.out.block.switches(dat[dat$sub == "307",],90)
```

```{r clean_switching_data_308, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-308'}
switch.rows$num[switch.rows$sub == "308"] = clean.out.block.switches(dat[dat$sub == "308",],90)
```

```{r clean_switching_data_309, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-309'}
switch.rows$num[switch.rows$sub == "309"] = clean.out.block.switches(dat[dat$sub == "309",],90)
```


```{r clean_switching_data_310, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-310'}
switch.rows$num[switch.rows$sub == "310"] = clean.out.block.switches(dat[dat$sub == "310",],85)
```

```{r clean_switching_data_311, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-311'}
switch.rows$num[switch.rows$sub == "311"] = clean.out.block.switches(dat[dat$sub == "311",],80)
```

```{r clean_switching_data_312, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-312'}
switch.rows$num[switch.rows$sub == "312"] = clean.out.block.switches(dat[dat$sub == "312",],90)
```

```{r clean_switching_data_313, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-313'}
switch.rows$num[switch.rows$sub == "313"] = clean.out.block.switches(dat[dat$sub == "313",],90)
```


```{r clean_switching_data_314, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-314'}
switch.rows$num[switch.rows$sub == "314"] = clean.out.block.switches(dat[dat$sub == "314",],90)
```


```{r clean_switching_data_315, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-315'}
switch.rows$num[switch.rows$sub == "315"] = clean.out.block.switches(dat[dat$sub == "315",],90)

```


```{r clean_switching_data_316, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-316'}
switch.rows$num[switch.rows$sub == "316"] = clean.out.block.switches(dat[dat$sub == "316",],90)

```


```{r clean_switching_data_317, warning = FALSE, eval = TRUE,echo = FALSE, fig.cap='sub-317'}
switch.rows$num[switch.rows$sub == "317"] = clean.out.block.switches(dat[dat$sub == "317",],90)

```

```{r clean_switching_data_318, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-318'}
switch.rows$num[switch.rows$sub == "318"] = clean.out.block.switches(dat[dat$sub == "318",],90)

```

```{r clean_switching_data_320, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-320'}
switch.rows$num[switch.rows$sub == "320"] = clean.out.block.switches(dat[dat$sub == "320",],75)

```

```{r clean_switching_data_321, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-321'}
switch.rows$num[switch.rows$sub == "321"] = clean.out.block.switches(dat[dat$sub == "321",],90)

```

```{r clean_switching_data_323, warning = FALSE, eval = TRUE, echo = FALSE, fig.cap='sub-323'}
switch.rows$num[switch.rows$sub == "323"] = clean.out.block.switches(dat[dat$sub == "323",],90)

```


```{r rem_post_switch, eval = TRUE, echo = FALSE}
# __remove trials occurring prior to the break point__

rem.post.switch <- function(data, rows){
  
    n_row = rows$num[rows$sub == data$sub[1]]
    trials = length(data$sub)
    mark.trials = array(data=0, dim=trials)
    for (x in 2:(trials - 25)){
      if (data$fixprob[x-1] != data$fixprob[x]){
        trials_rem = which(data$resp[c(x:(x+50))] == data$cor_resp[c(x:(x+50))])
        trials_rem = trials_rem[n_row]
        mark.trials[c(x:(x+trials_rem-1))] = 1
      }}
    data$mark = mark.trials
    data = data[data$mark < 1, ]
    return(data)
}

tmp = by(dat, dat$sub, rem.post.switch, switch.rows)
dat = as.data.frame(do.call(rbind, tmp))
rm(tmp)
```

__save data for analysis__ 
```{r save_dat, warning = FALSE, echo = FALSE}
# save.image("exp3_clean_BS_fv_18_03_17.R")
```

